\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-05-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
added description of utils/strike_dip_rake_to_CMTSOLUTION.c

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
%%%\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.eps}
\includegraphics[width=2.5in]{figures/gauss_vs_triangle_mod.pdf}
\par\end{centering}

\caption{Comparison of the shape of a triangle and the Gaussian function actually
used.}

\label{fig:gauss.vs.triangle}
\end{figure}

>>>>

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
\includegraphics[width=2.5in]{figures/gauss_vs_triangle_mod.pdf}
\par\end{centering}
\caption{Comparison of the shape of a triangle and the Gaussian function actually used.}
\label{fig:gauss.vs.triangle}
\end{figure}

If you know the earthquake source in strike/dip/rake format rather than in \texttt{CMTSOLUTION} format,
use the C code \texttt{SPECFEM3D\_GLOBE/utils/strike\_dip\_rake\_to\_CMTSOLUTION.c} to convert it.
The conversion formulas are given for instance in \cite{AkRi80}.
Note that the \cite{AkRi80} convention is slightly different from the Harvard \texttt{CMTSOLUTION} convention
(the sign of some components is different). The C code outputs both.
